---
title: "Reproducible Research and ECON 407 Problem Sets"
output: pdf_document
---

From [Wikipedia](https://en.wikipedia.org/wiki/Reproducibility#
Reproducible_research), reproducible research is defined as:


>The term reproducible research refers to the idea that the ultimate product of
academic research is the paper **along with** the full computational
environment used to produce the results in the paper such as the code, data,
etc. that can be used to reproduce the results and create new work based on the
research.

The reproducible research movement (especially for the statistical sciences)
takes this a step further by advocating for dynamic documents. The idea is
that a researcher should provide a file (the dynamic document) that can execute
the statistical analysis, generate figures, and contains accompanying text
narrative.  This file can be executed to produce the **academic paper**.  The
researcher shares this file with other researchers rather than the only the
paper.  It is my view that within 20 years nearly every scientific journal in
applied statistics will require this approach.

This document shows how to use `RMarkdown`
and markdown syntax.  The idea behind `RMarkdown` is that you share your research
by sharing your program file.  This file performs the full suite of statistical
analysis and can produce the pdf or MS Word document describing your analysis.
You will use this workflow for producing pdf or word documents for class
assignments.

For every problem set, you will turn in

* The `Rmarkdown` file containing all commands and written text that produces
your problem set responses. [the `R` file]
* A hardcopy of the pdf version produced after running your do file
[the hardcopy]
* The only exception to this rule is for questions involving proofs or other
equation heavy assigments where handwritten responses can be
attached to the hardcopy problem set response.


# Some Features of `RMarkdown`
RMarkdown allows for most features of
[Markdown](https://daringfireball.net/projects/markdown/syntax),
which is a liteweight and readable **text-based** language that allows
files to be easily converted to nice looking pdf, html, or even word
documents. Some features you will likely want to use:

* Equations and Math Notation using latex math
* Headers
* Emphasizing text (bold and italics)
* Numeric and bulletted lists
* Turning stata output on and off

# A simple example analysis using `Rmarkdown`

Below we'll be modeling the following regression equation for cars back in the day:

$$
price_i = \beta_0 + \beta_1 mpg_i + \beta_2 foreign_i + \epsilon_i
$$

## Load Data and Summarize
```{r}
auto = read.csv("http://rlhick.people.wm.edu/econ407/data/auto.csv")
summary(auto)
hist(auto$price)
```


### Regression Model

Here are the regression results:

```{r}
summary(lm(price~mpg+foreign,data=auto))
```

### Discussion

Looks like back in the day, foreign cars sell for more!

## Document Source
This document was written and generated entirely within `R`.